X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader

### 2013-04-15 paper/paper.tex
Fixed images so they take up the whole page

\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{images/xtoon_shading_alpha}
	\caption{Transparent tone detail texture}
	\label{fig:transparent_tone}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=5.5in]{images/hologram}
	\caption{Hologram result}
	\label{fig:hologram}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=4in]{images/inverse_lighting}
	\caption{Inverse Lighting result}
	\label{fig:inverseLighting}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=4in]{images/lighting}
	\caption{Lighting result}
	\label{fig:lightingResult}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=4in]{images/xtoon_shading_gradient}
	\caption{Tone texture for lighting}
	\label{fig:gradient}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=4in]{images/stipple-hatch-result1}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=6in]{images/stipple-hatch-result2}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch2}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=4in]{images/test}
  \caption{Sample illustration}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[width=4in]{images/alpha_issues}
 \caption{Issues with alpha blending. The vertices on the front of the model can still be seen.}
 \label{fig:alpha_issue}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Frames per second (FPS) of each new technique compared to original X-Toon shading}
	\label{tab:fps}
	\begin{tabular}{cccc}
		\hline
    		Method  & FPS (average) & FPS (max) & \% difference \\
		\hline\hline \\
    		Original X-Toon  & 1348 & 1420  & -                     \\
    		Light Direction & 1323 & 1435 & -1.85                     \\
		Angle & 1354 & 1447 & 0.45 \\
		Texture Blending & 1347 & 1430 & -0.07 \\
		Transparency & 1345 & 1419 & -0.22 \\
		\hline
	\end{tabular}
\end{table}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/xtoon_shading_alpha}
	\caption{Transparent tone detail texture. Note: the gray represents the transparency in the image.}
	\label{fig:transparent_tone}
\end{figure}

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/hologram}
	\caption{Hologram result}
	\label{fig:hologram}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/inverse_lighting}
	\caption{Inverse Lighting result}
	\label{fig:inverseLighting}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/lighting}
	\caption{Lighting result}
	\label{fig:lightingResult}
\end{figure*}

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/xtoon_shading_gradient}
	\caption{Tone texture for lighting}
	\label{fig:gradient}
\end{figure}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result1}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch1}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result2}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch2}
\end{figure*}

\begin{figure*}[h]
  \centering
  \includegraphics[width=5.5in]{images/test}
  \caption{Sample illustration}
\end{figure*}

\begin{figure*}[h]
 \centering
 \includegraphics[width=5.5in]{images/alpha_issues}
 \caption{Issues with alpha blending. The vertices on the front of the model can still be seen.}
 \label{fig:alpha_issue}
\end{figure*}

@@

\begin{table}
	\centering
	\caption{Frames per second (FPS) of each new technique compared to original X-Toon shading}
	\label{tab:fps}
	\begin{tabular}{cccc}
		\hline
    		Method  & FPS (avg) & FPS (max) & \% difference \\
		\hline\hline \\
    		Original X-Toon  & 1348 & 1420  & -                  \\
    		Light Direction & 1323 & 1435 & -1.85                \\
		Angle & 1354 & 1447 & 0.45 \\
		Texture Blending & 1347 & 1430 & -0.07 \\
		Transparency & 1345 & 1419 & -0.22 \\
		\hline
	\end{tabular}
\end{table}
